---
title: "Cross-Validation"
author:  "Alexey Abramov"
date: "11/24/2020"
output: 
  github_document:
    toc: true
---

# Setup

```{r, setup}
library(tidyverse)
library(p8105.datasets)
library(modelr)
library(mgcv)
library(readr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%"
)

theme_set(
  ggthemes::theme_fivethirtyeight() + theme(legend.position = "bottom")
  )

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.colour = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Simulated dataset

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )
```

```{r}
nonlin_df %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() 
```

## Cross- validation

Get training and testing datasets.

```{r}
train_df = sample_n(nonlin_df, size = 80)
test_df = anti_join(nonlin_df, train_df, by = "id")
```

Fit three models

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = gam(y ~ s(x), data = train_df)
wiggly_mod = gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

Let's see this graphically

Linear

```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")
```

Smooth
```{r}
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")
```

Wiggly
```{r}
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red")
```

Multiple predictions? Sure. Let's see all of them.

```{r}
train_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(. ~ model)
```

Now considering prediction accurary.

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

# Cross-validation with modelr package

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100)
```

What is happening here...
And then we bring it out and show it as a tibble so we can see the lists and dataframes.

They're stored as 'resample' which is a way of storing rows of data that is more efficient.  

```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble()
```


This step is only necessary for the gam function which requires a tibble, and won't work for list columns.

```{r}
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
    )
```

Let's try to fit models and get RMSEs for them.


```{r}
cv_df = 
  cv_df %>% 
  mutate(
    linear_mod = map(.x = train, ~lm(y ~ x, data = .x)),
    smooth_mod = map(.x = train, ~gam(y ~ s(x), data = .x)),
    wiggly_mod = map(.x = train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))
    ) 
```

map2 is used because we have two inputs into our iteration argument.

map2_dbl is a way to see the actual number.

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    rmse_linear = map2_dbl(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = smooth_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_wiggly = map2_dbl(.x = wiggly_mod, .y = test, ~rmse(model = .x, data = .y))
  )
```

What do these results say about the model choices?
Pivoting to tidy the dataset.  

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

The smooth model appears to be doing better.  

Here we group_by and summarize to show the means. 

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  group_by(model) %>% 
  summarize(avg_rmse = mean(rmse))
```


# Loading the data.

```{r}
child_growth_df =
  read_csv("./data/nepalese_children.csv")
```

Weight vs. arm circumference

This looks like it may have a curve in it.  
Linear? unlikely.
Line by line?  Maybe
Or smooth.

```{r}
child_growth_df %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = 0.3)
```

Updating dataframe to include a change point at 7 = "change point"

```{r}
child_growth_df = 
  child_growth_df %>% 
  mutate(
    weight_cp = (weight > 7) * (weight - 7)
  )
```

Starting to build models. 

Linear model

```{r}
linear_mod = lm(armc ~ weight, data = child_growth_df)
```

Smooth model

```{r}
smooth_mod = gam(armc ~ s(weight), data = child_growth_df)
```

Piecewise model

```{r}
pwlin_mod = lm(armc ~ weight + weight_cp, data = child_growth_df)
```

```{r}
child_growth_df %>% 
  gather_predictions(linear_mod, smooth_mod, pwlin_mod) %>% 
  ggplot(aes(x = weight, y = armc)) +
  geom_point(alpha = 0.3) +
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(. ~ model)
```

Ok, now let's try to understand it.

```{r}
cv_df = 
  crossv_mc(child_growth_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    linear_mod = map(.x = train, ~lm(armc ~ weight, data = .x)),
    smooth_mod = map(.x = train, ~gam(armc ~ s(weight), data = .x)),
    pwlin_mod = map(.x = train, ~lm(armc ~ weight + weight_cp, data = .x))
    ) %>% 
  mutate(
    rmse_linear = map2_dbl(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(.x = smooth_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_pwlin = map2_dbl(.x = pwlin_mod, .y = test, ~rmse(model = .x, data = .y))
  )
```

Violin plot of RMSEs

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

